---
title: "Collaborative Coding"
output: html_document
---

# Analysis of *Intro Survey Data*

&nbsp;

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Initial set up

# needed libraries
library(dplyr)
library(plotly)
library(knitr)

# sources
source('scripts/analysis.R')
source('scripts/chart1.R')
source('scripts/chart2.R')

# Data set
dataset <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-survey-data/master/intro_survey_data.csv")

# Get information about data set
info_list <- info_function(dataset)

# Get cleaned data from returned info
data <- info_list$data
```

#### In the **INFO498f** class, there are **`r info_list$rows`** students who completed the survey. The class is composed of: 
`r kable(info_list$class_standing)`

&nbsp;

These students were asked to complete a **`r info_list$columns`** question survey at the beginning of the quarter. Below is an analysis of their answers.

### Chart 1

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Builds first chart
build_chart(info_list$r_exp_by_standing)

```


### Chart 2

This is a box chart showcasing the total countries visited by students based off class standing.
```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Builds second chart
build_second_chart(data)
```